### 2025-05-05 backmatter/solutions.tex
First draft final edits
Pre-correction version of thesis

\begingroup
\renewcommand{\theequation}{\Aleph{chapter}.\arabic{equation}}

@@

% ---------------------------------------
\Soln{Factorization of Collinear Phase Space}{phase-space-factorization}
% ---------------------------------------

@@

Note that the only way to produce a \(\widetilde{\mathcal{M}}_{m \to n}\), at least perturbatively, is to use the cubic vertex of \phicubedsix{} to produce new outgoing lines from lower-order amplitudes:
\begin{align}
    \widetilde{\mathcal{M}}_{m\to n}(p_1,\cdots,p_m;\,k_1,\cdots,k_n)
    \,\,
    =
    \begin{tikzpicture}[baseline={(0,-0.1)}]
        \begin{feynman}
            \node[blob] (mid) {};
            \vertex (a) [above left=of mid] {\(p_1\)};
            \vertex (ap) [below right=.5cm and .5cm of a];
            \vertex (b) [below left=of mid] {\(p_m\)};
            \vertex (c) [above right=of mid] {\(k_n\)};
            \vertex (cp) [below=.7cm of c] {\(k_{n-1}\)};
            \vertex (d) [below right=of mid] {\(k_1\)};
            \node[below=1cm of a] (L) {\(\vdots\)};
            \node[below=1.2cm of c] (L) {\(\vdots\)};
            \diagram* {
                (a) -- (mid) -- (b),
                (d) -- (mid),
                (ap) -- (c),
                (mid) -- (cp),
            };
        \end{feynman}
    \end{tikzpicture}
    \quad
    +
    \quad
    \begin{tikzpicture}[baseline={(0,-0.1)}]
        \begin{feynman}
            \node[blob] (mid) {};
            \vertex (a) [above left=of mid] {\(p_1\)};
            \vertex (b) [below left=of mid] {\(p_m\)};
            \vertex (cpp) [above right=.4cm and .4cm of mid];
            \vertex (c) [above right=.3cm and .6cm of cpp] {\(k_n\)};
            \vertex (cp) [right=.6cm of cpp] {\(k_{n-1}\)};
            \vertex (d) [below right=of mid] {\(k_1\)};
            \node[below=1cm of a] (L) {\(\vdots\)};
            \node[below left=1.2cm and .3cm of c] (L) {\(\vdots\)};
            \diagram* {
                (a) -- (mid) -- (b),
                (d) -- (mid),
                % (cp) -- (cpp) -- (c)
                (cp) -- (cpp) -- (c),
                (mid) -- (cpp),
            };
        \end{feynman}
    \end{tikzpicture}
    \quad
    +
    \quad
    \cdots
    ,
    \label{eq:eikonal_diagram}
\end{align}
where the ellipses include the diagrams where \(k_n\) branches off of any of the external lines of the lower point amplitude.

@@

Therefore,
\begin{align}
    \dd\sigma_n
    =
    \dd \sigma_{n-1}
    \,\,
    \times
    \,\,
    \frac{g^2 E^{d-6}}{4\le(2\pi\ri)^{d-1}}
    \,\,
    \Omega_{d-3}
    \,\,
    \times
    \,\,
    \le(
        \dd x
        \,
        \le( x (1-x) \ri)^{d-5}
    \ri)
    \,\,
    \times
    \,\,
    \le(
        \frac{\dd\theta}{\theta^{7-d}}
    \ri)
    ,
\end{align}
and in \(\phicubedsix{}\),
\begin{align}
    \dd\sigma_n
    =
    \dd \sigma_{n-1}
    \,\,\,
    2 a_g
    \,\,
    \dd x\,\, p(x)
    \,\,\,
    \frac{\dd \theta}{\theta^{7-d}}
    =
    \dd \sigma_{n-1}
    \,\,\,
    2 a_g
    \,\,
    \dd x\,\, p(x)
    \,\,\,
    \frac{\dd \theta}{\theta}
    ,
\end{align}
where we have defined
\begin{align}
    a_g
    =
    \frac{g^2\Omega_{d-3}}{4 \le(2 \pi\ri)^{d-1}}
    =
    g^2 \Omega_3 / 256 \pi^5 = g^2 / 128 \pi^3
    \,,
\end{align}
where as before, the final equality holds in \(d=6\) dimensions -- this is the \phicubedsix{} analogue of \(a_s = g_s^2 \Omega_2 / 64 \pi^3 = g_s^2 / \le(4 \pi\ri)^2\) in \gls{qcd} -- and the \glslink{splittingfn}{\vocab{splitting function}} \(p(x)\) is
\begin{align}
    p(x)
    =
    \frac{g^2\Omega_{d-3}}{4 \le(2 \pi\ri)^{d-1}}
    x^{d-5}(1-x)^{d-5}
    =
    x(1-x)
    \,,
\end{align}
where the final equality holds again in \(d=6\) dimensions.

@@

% ---------------------------------------
% \Soln{Splitting Functions of the SM I: QED}{massless-qed}
% ---------------------------------------

@@

% ---------------------------------------
\Soln{Regimes and Accuracy}{accuracy}
% ---------------------------------------

% ---------------------------------------
\Soln{No Emission Probability}{no-emission}
% ---------------------------------------

% ---------------------------------------
\Soln{Fragmentation in a Parton Shower}{p2p-fragmentation}
% ---------------------------------------

% ---------------------------------------
\Soln{Fragmentation of Partons into Hadrons}{p2h-fragmentation}
% ---------------------------------------

% TODO: go through and fix
\sam{right now, soft drop; want general}

For the sake of completeness, let us go through the the derivation of the Soft Drop expression for the multiple emissions Sudakov exponent. We take the explicit form of the Sudakov exponent as
\begin{align}
    \Sigma\left(C_1^{(\beta)}\right) &= \sum_{n = 1}^\infty \prod_{m = 1}^n \left[\int_0^{1} \frac{d\theta'_m}{\theta'_m}\int_0^1 dz_m p_i(z_m) \frac{\alpha_S(\kappa_m)}{\pi}\Theta(z_m - z_c) \Theta(\theta_{m-1} - \theta_m)\right]
    \\
    &\ \ \ \ \times\Theta\left(C_1^{(\beta)} - \sum_{m=1}^n z_m (\theta'_m)^\beta\right) \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right]
\end{align}
where we impose angular ordering with the \(\Theta(\theta_{i-1} - \theta_i)\). Notice that the Laplace transform of this expression is
\begin{align}
    \tilde\Sigma(\nu) &= \int_{-\infty}^\infty d C_1^{(\beta)} \Sigma(C_1^{(\beta)}) e^{-\nu C_1^{(\beta)}}
    \\
    &= \sum_{n=1}^\infty \prod_{m=1}^n  \left[\int_0^{1} \frac{d\theta'_m}{\theta'_m}\int_0^1 dz_m p_i(z_m) \frac{\alpha_S(\kappa_m)}{\pi}\Theta(z_m - z_c) \Theta(\theta_{i-1} - \theta_i)\right]\\
    &\ \ \ \ \ \times \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right] \times\int^\infty_{C_{\rm max}} dC_1^{(\beta)} e^{-v C_1^{(\beta)}}
\end{align}
where \(C_{\rm max} = \sum_m z_m (\theta'_m)^\beta\), and we have used the \(\Theta\) function. Performing the integral over \(C_1^{(\beta)}\), we have
\begin{align}
    \tilde\Sigma(\nu) &= -\frac{1}{\nu} \sum_{n=1}^\infty \prod_{m=1}^n  \left[\int_0^{1} \frac{d\theta'_m}{\theta'_m}\int_0^1 dz_m p_i(z_m) \frac{\alpha_S(\kappa_m)}{\pi}\Theta(z_m - z_c) \Theta(\theta_{i-1} - \theta_i)\right]\\
    &\ \ \ \ \ \times \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right] \times \exp\left[ -\nu \sum_m z_m(\theta'_m)^\beta\right]
    \\
    &= -\frac{1}{\nu} \sum_{n=1}^\infty \frac{1}{n!}\left(\int_0^{1} \frac{d\theta'}{\theta'}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c) \right)^n\\
    &\ \ \ \ \ \times \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right] \times \exp\left[ -\nu \sum_m z_m(\theta'_m)^\beta\right]
    \\
    &= -\frac{1}{\nu} \sum_{n=1}^\infty \frac{1}{n!}\left(\int_0^{1} \frac{d\theta'}{\theta'}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c) \times e^{-\nu z (\theta')^\beta}\right)^n\\
    &\ \ \ \ \ \times \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right]
    \\
    &=  -\frac{1}{\nu} \exp\left[\int_0^{1} \frac{d\theta'}{\theta'}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c) \left( e^{-\nu z (\theta')^\beta} - 1 \right)\right]
\end{align}
where we have gained an extra \(\frac{1}{n!}\) by eliminating the angular ordering in the second equality. By replacing \(\beta\) with \(\alpha\), and the theta function \(\Theta(z - z_c)\) with \(\Theta(z - z_c (\theta')^\beta)\), we recover Soft Drop Equations (3.11) and (3.12) (up to a minus sign in the inverse Laplace transform, is this fixed by our clockwise contour?).

\textbf{LO Result}
Following Soft Drop, we write then that
\begin{align}
    \Sigma(C_1^{(\beta)}) = \int \frac{d\nu}{2\pi i\nu} e^{\nu C_1^{(\beta)}} e^{-R(\nu^{-1})}
    % \label{eqn:inverseLaplace}
\end{align}
with
\begin{align}
    R(\nu^{-1}) = \int_0^1\frac{d\theta'}{\theta'}\int_0^1 dz p(z) \frac{\alpha_s(\kappa)}{\pi}\Theta(z-z_c)\left(1 - e^{-\nu z (\theta')^\beta} \right)
\end{align}
As discussed by Soft Drop and \href{https://arxiv.org/pdf/hep-ph/9801324.pdf}{9801324} , we use the method of steepest descent to evaluate this integral, and do so at \(C_1^{(\beta)} = \nu^{-1}\). Furthermore, we approximate
\begin{align}
    1 - e^{-\nu \xi} \to \Theta(\xi - \nu^{-1})
    % \label{theta_approx_1}
\end{align}
for large \(\nu\). We will take into account the corrections to this later. Then
\begin{align}
    R(\nu^{-1}) \to \int_0^1\frac{d\theta'}{\theta'}\int_0^1 dz p(z) \frac{\alpha_s(\kappa)}{\pi}\Theta(z-z_c) \Theta(z (\theta')^\beta - \nu^{-1})
\end{align}
As in Section \ref{sec:MLLNew}, we may perform the change of variables \(c = z(\theta')^{\beta}\), for which we have that
\begin{align}
    R(\nu^{-1}) \cong \int_{\nu^{-1}}^1 \frac{dc}{c} \phi(c^{-1}) = R_{LO}(\nu^{-1})
\end{align}
where we have defined
\begin{align}
    \phi(c^{-1}) = \frac{1}{\beta}\int_{\max(c, z_c)}^1 dz p_i(z) \frac{\alpha_s(\kappa)}{\pi}
\end{align}
such that our LO result is proportional to
\begin{align}
    \Sigma(C_1^{(\beta)}) \sim e^{- \int_{C_1^{(\beta)}}^1 dc \phi(c^{-1})} = e^{-R_{LO}(C_1^{(\beta)})} \approx e^{-R(C_1^{(\beta)})}
\end{align}

\textbf{Next Order Corrections}
We may improve this by including corrections of the form
\begin{align}
    R(\nu^{-1}) = R_{LO}(\nu^{-1}) + \delta R(\nu^{-1})
\end{align}
with
\begin{align}
    R_{LO}(\nu^{-1}) &= \int_{\nu^{-1}}^1 \frac{dc}{c} \phi(c^{-1})
    \\
    \delta R(\nu^{-1}) &= -\int_{\nu^{-1}}^1 \frac{dc}{c} \phi(c^{-1}) + \int_0^1 \frac{dc}{c} \phi(c^{-1}) \left( 1 - e^{-c \nu} \right)
\end{align}
where the second equation takes into account corrections from our earlier approximation in Equation \ref{theta_approx_1}.
Let us define now \(x = c \nu\), so that
\begin{align}
    \delta R(\nu^{-1}) = \int_0^{\nu} \frac{dx}{x} \phi(\nu/x) \left( 1 - e^{-x}\right) - \int_1^\nu \frac{dx}{x} \phi(\nu/x)
\end{align}
Simplifying and regulating the integral with dimensional regularization, we have
\begin{align}
    \delta R(\nu^{-1}) = \int_0^{1} \frac{dx}{x} \phi(\nu/x) x^\epsilon - \int_0^\nu \frac{dx}{x} \phi(\nu/x) x^\epsilon e^{-x}
    % \label{eqn:nextorderintegrals}
\end{align}
Notice next that
\begin{align}
    \partial_\nu R_{LO}(\nu^{-1}) =  -\frac{1}{\nu^{-1}} \phi(\nu) \cdot (-\frac{1}{\nu^2})
\end{align}
so that
\begin{align}
    \frac{\partial R_{LO}(\nu^{-1})}{\partial \log(\nu)} = \phi(\nu)
\end{align}
%\Comment{I'm a little worried in our case that \(\phi\) may depend on \(\nu\) which might lead to additional terms. Probably fine, and so pushing ahead for now.} Nope! It's pretty clear that the only \(\nu\) dependence is where we've put it! Great!
We may approximate the integrals in Equation \ref{eqn:nextorderintegrals} by replacing \(\phi(\nu/x)\) by its value at \(x = 1\). We may use further
\begin{align}
    \int_0^1\frac{dx x^\epsilon}{x} - \int_0^\infty\frac{dx x^\epsilon}{x}e^{-x} = \frac{1}{\epsilon} - \Gamma(\epsilon) = \gamma_E + \mathcal{O}(\epsilon)
    % \label{eqn:dimregint1}
\end{align}
to see that, in the large \(\nu\) limit,
\begin{align}
    \delta R(\nu^{-1}) = \int_0^{1} \frac{dx}{x} \phi(\nu/x) x^\epsilon - \int_0^\nu \frac{dx}{x} \phi(\nu/x) e^{-x} x^\epsilon \cong \gamma_E R'(\nu^{-1}) = \delta R^{(1)}(\nu^{-1})
\end{align}
with \(R'(\nu^{-1}) = \partial R_{LO}(\nu^{-1}) / \partial \log(\nu)\). In the region of integration for which \(\nu^{-1}\approx C_1^{(\beta)}\), we can wave our hands a bit and write that, up to subleading corrections, we may replace \(R'(\nu^{-1})\) by
\begin{align}
    R'(C_1^{(\beta)}) = \frac{\partial R (C_1^{(\beta)})}{\partial \log(1/C_1^{(\beta)})} = -\frac{\partial R (C_1^{(\beta)})}{\partial \log(C_1^{(\beta)})}
\end{align}

\textbf{Denominator}:
The denominator that we see in, for example, Soft Drop, comes from the corrections to \(R_{LO}\). In particular, expanding in a Taylor series,
\begin{align}
    R(\nu^{-1}) = R_{LO}(C_1^{(\beta)}) + \log(C_1^{(\beta)} \nu) R'_{LO}(C_1^{(\beta)}) + \log(C_1^{(\beta)} \nu)^2 R''_{LO}(C_1^{(\beta)}) + \mathcal{O}(R'''_{LO}(C_1^{(\beta)}))
\end{align}
Then to a level of precision determined by \(R'\), we have
\begin{align}
    e^{-R(\nu^{-1})} \cong e^{-R(C) - \gamma_E R'(C)} (C_1^{(\beta)} \nu)^{-R'(C)}
\end{align}
We now notice that
\begin{align}
    \int \frac{d\nu}{2\pi i \nu} (C\cdot \nu)^{-\xi} e^{\nu C} = \int \frac{d\eta}{2\pi i \eta} \eta^{-\xi}e^\eta = \frac{1}{\Gamma(1 + \xi)}
\end{align}
as a special case of Equation (4.20) of \href{https://arxiv.org/pdf/hep-ph/9801324.pdf}{9801324} . We make this replacement in Equation (\ref{eqn:inverseLaplace}) above to find that, to \(\mathcal{O}(R')\), we have
\begin{align}
    \Sigma(C_1^{(\beta)}) \cong \frac{e^{-R(C) - \gamma_E R'(C)}}{\Gamma(1 + R'(C))}
\end{align}

% ---------------------------------------
% \Soln{Substructure with Multiple Emissions}{ungroomed-me}
% ---------------------------------------

% ---------------------------------------
\Soln{Multiplicity of Subjets}{subjet-multiplicity}
% ---------------------------------------

@@

    \item
    \label{item:LL_angularity_gen}
    The splitting of a parton is described by its angularity \(e^{(f)}_\varsigma\).
    %
    Using the techniques of the previous section, we may write the LL probability that there is no emission with angularity greater than \(e^{(f)}_\varsigma\), given that there has been an emission with angularity \(e^{(i)}_\varsigma\), as
    \begin{align}
        \label{eqn:alg_LLang_ratio}
        \mathbb{P}
        \left(
            {\rm no~emission~with~}e_\varsigma>e^{(f)}_\varsigma
            ~|~
            e_\varsigma < e^{(i)}_\varsigma
        \right)
        &=
        \frac{\Sigma(e^{(f)}_\varsigma)}{\Sigma(e^{(i)}_\varsigma)}
        \\
        \notag
        &=
        \exp\left[
            -\frac{C_R \alpha_s}{\varsigma~\pi}
            \left(
                \log^2(2 e^{(f)}_\varsigma) - \log^2(2 e^{(i)}_\varsigma)
            \right)
        \right]
        .
    \end{align}
    We can therefore sample from the corresponding probability distribution by the inverse transform method:
    %
    pick a random number \(r\) uniformly distributed between 0 and 1, and set it equal to the above cumulative distribution.
    %
    The corresponding value of \(e^{(f)}_\varsigma\) is
    \begin{align}
        \label{eqn:alg_LLang}
        e^{(f)}_\varsigma
        =
        \frac{1}{2}
        \exp\left[
            -\sqrt{\log^2(2 e^{(i)}_\varsigma) - \frac{\varsigma~\pi}{C_R \alpha_s} \log(r)}
        \right]
        ,
    \end{align}
    which is taken to be the angularity of the splitting from this mother parton.

@@

We can also extend this procedure to include running coupling effects and non-singular pieces of the splitting function, which contribute to MLL accuracy.
%
We produce these higher-order effects by using veto method sampling \cite{Sjostrand:2007gs,Larkoski:2013paa,Sjostrand:2014zea}:
%
\begin{enumerate}
	\item
	\label{item:MLL_ps_start}
	Generate an angularity, angle, and energy fraction with Steps \ref{item:LL_ps_start}--\ref{item:LL_ztheta_sampling} of the LL parton shower algorithm, with the coupling \(\alpha_s\) of \Eqs{alg_LLang_ratio}{alg_LLang} replaced by a large fixed coupling \(\hat\alpha = \frac{1}{2}\).

>>>>

\begingroup
\renewcommand{\theequation}{\Alph{chapter}.\arabic{equation}}

@@

@@

Note that the only way to produce a \(\widetilde{\mathcal{M}}_{m \to n}\), at least perturbatively, is to use the cubic vertex of \phicubedsix{} to produce new outgoing lines from lower-order amplitudes:
\begin{align}
    \label{eq:eikonal_diagram}
    \widetilde{\mathcal{M}}_{m\to n}(p_1,\cdots,p_m;\,k_1,\cdots,k_n)
    \,\,
    =
    \begin{tikzpicture}[baseline={(0,-0.1)}]
        \begin{feynman}
            \node[blob] (mid) {};
            \vertex (a) [above left=of mid] {\(p_1\)};
            \vertex (ap) [below right=.5cm and .5cm of a];
            \vertex (b) [below left=of mid] {\(p_m\)};
            \vertex (c) [above right=of mid] {\(k_n\)};
            \vertex (cp) [below=.7cm of c] {\(k_{n-1}\)};
            \vertex (d) [below right=of mid] {\(k_1\)};
            \node[below=1cm of a] (L) {\(\vdots\)};
            \node[below=1.2cm of c] (L) {\(\vdots\)};
            \diagram* {
                (a) -- (mid) -- (b),
                (d) -- (mid),
                (ap) -- (c),
                (mid) -- (cp),
            };
        \end{feynman}
    \end{tikzpicture}
    \quad
    +
    \quad
    \begin{tikzpicture}[baseline={(0,-0.1)}]
        \begin{feynman}
            \node[blob] (mid) {};
            \vertex (a) [above left=of mid] {\(p_1\)};
            \vertex (b) [below left=of mid] {\(p_m\)};
            \vertex (cpp) [above right=.4cm and .4cm of mid];
            \vertex (c) [above right=.3cm and .6cm of cpp] {\(k_n\)};
            \vertex (cp) [right=.6cm of cpp] {\(k_{n-1}\)};
            \vertex (d) [below right=of mid] {\(k_1\)};
            \node[below=1cm of a] (L) {\(\vdots\)};
            \node[below left=1.2cm and .3cm of c] (L) {\(\vdots\)};
            \diagram* {
                (a) -- (mid) -- (b),
                (d) -- (mid),
                % (cp) -- (cpp) -- (c)
                (cp) -- (cpp) -- (c),
                (mid) -- (cpp),
            };
        \end{feynman}
    \end{tikzpicture}
    \quad
    +
    \quad
    \cdots
    ,
\end{align}
where the ellipses include the diagrams where \(k_n\) branches off of any of the external lines of the lower point amplitude.

@@

Therefore,
\begin{align}
    \dd\sigma_n
    =
    \dd \sigma_{n-1}
    \,\,
    \times
    \,\,
    \frac{g^2 E^{d-6}}{4\le(2\pi\ri)^{d-1}}
    \,\,
    \Omega_{d-3}
    \,\,
    \times
    \,\,
    \le(
        \dd x
        \,
        \le( x (1-x) \ri)^{d-5}
    \ri)
    \,\,
    \times
    \,\,
    \le(
        \frac{\dd\theta}{\theta^{7-d}}
    \ri)
    ,
\end{align}
and in \(\phicubedsix{}\),
\begin{align}
    \dd\sigma_n
    =
    \dd \sigma_{n-1}
    \,\,\,
    2 a_g
    \,\,
    \dd x\,\, p(x)
    \,\,\,
    \frac{\dd \theta}{\theta^{7-d}}
    =
    \dd \sigma_{n-1}
    \,\,\,
    2 a_g
    \,\,
    \dd x\,\, p(x)
    \,\,\,
    \frac{\dd \theta}{\theta}
    ,
\end{align}
where we have defined
\begin{align}
    a_g
    =
    \frac{g^2\Omega_{d-3}}{4 \le(2 \pi\ri)^{d-1}}
    =
    g^2 \Omega_3 / 256 \pi^5 = g^2 / 128 \pi^3
    \,,
\end{align}
where as before, the final equality holds in \(d=6\) dimensions -- this is the \phicubedsix{} analogue of \(a_s = g_s^2 \Omega_2 / 64 \pi^3 = g_s^2 / \le(4 \pi\ri)^2\) in \gls{qcd} -- and the \glslink{splittingfn}{\vocab{splitting function}} \(p(x)\) is
%
\sam{TODO: fix incorrect phi-cubed splitting function}
\begin{align}
    p(x)
    =
    \frac{g^2\Omega_{d-3}}{4 \le(2 \pi\ri)^{d-1}}
    x^{d-5}(1-x)^{d-5}
    =
    x(1-x)
    \,,
\end{align}
where the final equality holds again in \(d=6\) dimensions.

@@

@@

% ---------------------------------------
\Soln{The No-Emission Probability}{no-emission}
% ---------------------------------------

In this problem, we derive the no-emission probability -- the probability that a partonic cascade contains no emission with some property.
%
We will be interested in particular in the probability that a cascade contains no emission with an angularity \(z_\text{soft} \theta^\varsigma > e_\sigma\).
%
Recall that \(z_\text{soft} := \min(z, 1-z)\).

The probability that there is no emission with a \textit{mass} greater than \(m^2\) will be similar, but we would need to invoke the strongly ordered limit to write the mass-squared of an emission as
\begin{align}
    m^2_{ij}
    =
    m^2_i + m^2_j + 2 \le(E_i E_j - \vec{p}_i \cdot \vec{p}_j\ri)
    \,
    \approx
    \,
    z_i\,z_j \theta^2_{ij}
    \approx
    z_\text{soft} \theta^2
    \,,
\end{align}
where \(i\) and \(j\) denote the children of an emission, and the strongly-ordered limit allows us to write \(m^2_{i,\,j} \ll z(1-z)\theta^2_{ij}\), as discussed in \Sec{parton-shower}, as well as \(z(1-z) \approx z_\text{soft}\) and \(\theta := \theta_{ij} \ll 1\).
%
Therefore, in the strongly-ordered limit, the probability that there is no emission in the cascade with \textit{mass} greater than \(m\) can be related to the probability that there is no emission with an angularity greater than \(e_\varsigma\), once we set \(\varsigma = 2\).

Next, we argue that the probability that there \textit{is} an emission with an angularity greater than \(e_\varsigma\) obeys a differential equation.
%
In particular, if \(e_\varsigma\) decreases slightly, then the probability that there is no emission with angularity greater than \(e_\varsigma\) \textit{also} decreases -- the phase space for such an emission becomes slightly larger.
%
The resulting differential equation for the no-emission probability can be written
\begin{align}
    \dv{\Pi_i(e_\varsigma)}{e_\varsigma}
    \,\,
    =
    \,\,
    \Pi_i(e_\varsigma)
    \,\,\times\,\,
    4
    \int_0^R \,\, \as \, \frac{\dd\theta}{\theta}
    \,\,
    \int_0^1 \dd z \sum_j p_{j \leftarrow i}(z)
    \,\,
    \delta(z\theta^\varsigma - e_\varsigma)
    \,,
\end{align}
which states that the no-emission probability decreases by an amount proportional to the probability that there \textit{is} an emission with angularity \(e_\varsigma\), and we have used the emission phase space derived in \Secs{splitting-functions}{parton-shower}.

Therefore,
\begin{align}
    \int_{e' = e_\varsigma} \dd \ln \Pi_i(e')
    =
    -\ln \Pi_i(e_\varsigma)
    =
    4
    \int_0^R \,\, \as \, \frac{\dd\theta}{\theta}
    \,\,
    \int_0^1 \dd z \sum_j p_{j \leftarrow i}(z)
    \,\,
    \le(
        1 -
        \Theta(e_\varsigma > z\theta^\varsigma)
    \ri)
    \,,
\end{align}
or
\begin{align}
    \ln \Pi_i(e_\varsigma)
    =
    -4
    \int_0^R \,\, \as \, \frac{\dd\theta}{\theta}
    \,\,
    \int_0^1 \dd z \sum_j p_{j \leftarrow i}(z)
    \,\,
    \Theta(e_\varsigma < z\theta^\varsigma)
    \,.
\end{align}

\begin{answer}
    We conclude that
    \begin{align}
        \Pi_i(e_\varsigma)
        =
        \exp
        \le[
            -4
            \int_0^R \,\, \as \, \frac{\dd\theta}{\theta}
            \,\,
            \int_0^1 \dd z \sum_j p_{j \leftarrow i}(z)
            \,\,
            \Theta(e_\varsigma < z\theta^\varsigma)
        \ri]
        \,.
    \end{align}
\end{answer}

At LL, we can write \(p_{j \leftarrow i} = 2 C_{R_i} / z \delta_{j\, g}\).
%
We can then write, approximating the bounds of integration on \(z_\text{soft}\) as ranging from 0 to 1 rather than 0 to 1/2,
\begin{align}
    \int_0^R \frac{\dd\theta}{\theta}
    \,
    \int_0^1 \frac{\dd z}{z}
    \,
    &
    \Theta(e_\varsigma < z\theta^\varsigma)
    \,
    =
    \,
    \frac{1}{\varsigma}
    \,
    \int_0^1 \frac{\dd z}{z}
    \,
    \int_0^{z R^\varsigma} \frac{\dd\theta}{\theta}
    \,
    \Theta(e_\varsigma < z\theta^\varsigma)
    \,
    =
    \,
    \frac{1}{\varsigma}
    \,
    \int_{e/R^\varsigma}^1 \frac{\dd z}{z}
    \,
    \ln\le(z R^\varsigma / e_\varsigma\ri)
    \,
    \\
    &=
    \,
    \frac{1}{2\,\varsigma}
    \,
    \ln^2\le(e_\varsigma / R^\varsigma\ri)
    \,.
\end{align}

\begin{answer}
    At LL accuracy, we therefore have
    \begin{align}
        \Pi_i(e_\varsigma)
        =
        \exp
        \le[
            -\frac{4\as C_{R_i}}{\varsigma}
            \ln^2\le(e_\varsigma / R^\varsigma\ri)
        \ri]
        \,.
    \end{align}
\end{answer}

% ---------------------------------------
\Soln{The Veto Algorithm for Generating Partonic Emissions}{veto-algorithm}
% ---------------------------------------
\begin{enumerate}[label=\alph*)]
    \item
        Note that
        \begin{align}
            \mathbb{P}(F^{-1}(u) < x)
            =
            \mathbb{P}(u < F(x))
            =
            F(x)
            \,,
        \end{align}
        since the probability that \(u\), which is uniformly distributed between 0 and 1, is less than \(F(x)\) (a number between 0 and 1) is simply \(F(x)\).

        Since \(X\) and \(F^{-1}(U)\) have the same cumulative distributions, they must also have the same probability distributions.
        %
        Therefore, by sampling the random variable \(U\) uniformly between 0 and 1 and computing \(F^{-1}(U)\), we obtain a random variable whose probability distribution is identical to that of \(X\), and this method (the inverse transform method) effectively samples from the probability distribution of \(X\).

        \item
            The random number generated by applying the given graphical depiction of the veto algorithm has the distribution
            \begin{align}
                \rho(x \, | \, T)
                =
                \int_0^T \dd t'
                \,
                g(t') \, \Pi_g (t' \, | \, T)
                \le(
                    \frac{f(t')}{g(t')}
                    \delta(x - t')
                    \,\,
                    +
                    \,\,
                    \le(1 - \frac{f(t')}{g(t')}\ri)
                    \,
                    \rho(x \, | \, t')
                \ri)
                \,,
            \end{align}
            where the factor of \(g(t') \Pi_g(t'|T)\) in the integrand is simply the probability distribution from which we are sampling, the first term in the parentheses are associated with the \textit{accept} step, and the second term in the parentheses is associated with the possibility of the \textit{veto}, after which we continue sampling from the \textit{new} distribution \(g(x) \Pi_g(x \, | \, t')\).

            To make progress, we take a derivative with respect to \(T\) to obtain
            \begin{align}
                \partial_T \rho(x \, | \, T)
                =
                f(T) \delta(x - T)
                \,\,
                +
                \,\,
                \le(g(T) - f(T)\ri)
                \,
                \rho(x \, | \, T)
                \,\,
                -
                \,\,
                g(T) \rho(x\,|\,T)
            \end{align}
            where the final term comes from the derivative of \(\Pi_g(t'\, | \, T)\) \textit{within} the integrand -- \(\partial_T \Pi_g(t'\,|\,T) = -g(T) \Pi_g(t'\,|\,T)\) -- and in the remaining terms we have used that \(\Pi_g(T\,|\,T) = 1\).
            %
            Combining terms yields
            \begin{align}
                \partial_T \rho(x \, | \, T)
                =
                f(T) \le(
                    \delta(x - T)
                    -
                    \rho(x \, | \, T)
                \ri)
                \,,
            \end{align}
            or
            \begin{align}
                e^{-\int_x^T f(t') \dd t'}
                \partial_T \le(
                    e^{\int_x^T f(t') \dd t'} \, \rho(x \, | \, T)
                \ri)
                =
                f(T) \delta(x - T)
                \,.
            \end{align}
            Re-ordering, exchanging \(T\) for a dummy variable \(T'\), and integrating over \(T'\) from \(x-\epsilon\) to \(T\), we obtain
            \begin{align}
                \exp\le[\int_x^{T'} f(t') \dd t'\ri]
                \rho(x \, | \, T')
                \Big|^{T'=T}_{T'=x-\epsilon}
                =
                f(x)
                \,.
            \end{align}
            The bound of integration of \(x - \epsilon\) ensures that the delta function integrates to one, and additionally allows us to use that \(\rho(x \, | \, x - \epsilon) = 0\), since \(\rho(x\,|\,T)\) is associated with the probability distribution for sampling a value of \(x\) smaller than \(T\) by definition.

            We conclude that
            \begin{align}
                \rho(x \, | \, T)
                =
                f(x)
                \exp\le[-\int_x^{T} f(t') \dd t'\ri]
                \,,
            \end{align}
            which is indeed the desired probability distribution.
\end{enumerate}

@@

    \item
    \label{item:LL_angularity_gen}
    The splitting of a parton is described by its angularity \(e^{(f)}_\varsigma\).
    %
    Using the techniques of the previous section, we may write the LL probability that there is no emission with angularity greater than \(e^{(f)}_\varsigma\), given that there has been an emission with angularity \(e^{(i)}_\varsigma\), as
    \begin{align}
        \label{eq:alg_LLang_ratio}
        \mathbb{P}
        \left(
            {\rm no~emission~with~}e_\varsigma>e^{(f)}_\varsigma
            ~|~
            e_\varsigma < e^{(i)}_\varsigma
        \right)
        &=
        \frac{\Sigma(e^{(f)}_\varsigma)}{\Sigma(e^{(i)}_\varsigma)}
        \\
        \notag
        &=
        \exp\left[
            -\frac{C_R \alpha_s}{\varsigma~\pi}
            \left(
                \log^2(2 e^{(f)}_\varsigma) - \log^2(2 e^{(i)}_\varsigma)
            \right)
        \right]
        .
    \end{align}
    We can therefore sample from the corresponding probability distribution by the inverse transform method:
    %
    pick a random number \(r\) uniformly distributed between 0 and 1, and set it equal to the above cumulative distribution.
    %
    The corresponding value of \(e^{(f)}_\varsigma\) is
    \begin{align}
        \label{eq:alg_LLang}
        e^{(f)}_\varsigma
        =
        \frac{1}{2}
        \exp\left[
            -\sqrt{\log^2(2 e^{(i)}_\varsigma) - \frac{\varsigma~\pi}{C_R \alpha_s} \log(r)}
        \right]
        ,
    \end{align}
    which is taken to be the angularity of the splitting from this mother parton.

@@

We can also extend this procedure to include running coupling effects and non-singular pieces of the splitting function, which contribute to MLL accuracy.
%
We produce these higher-order effects by using veto method sampling \cite{Sjostrand:2007gs,Larkoski:2013paa,Sjostrand:2014zea}:
%
\begin{enumerate}
	\item
	\label{item:MLL_ps_start}
	Generate an angularity, angle, and energy fraction with Steps \ref{item:LL_ps_start}--\ref{item:LL_ztheta_sampling} of the LL parton shower algorithm, with the coupling \(\alpha_s\) of \Eqs{alg_LLang_ratio}{alg_LLang} replaced by a large fixed value for the coupling, \(\hat\alpha = \frac{1}{2}\).
